### 2015-06-13 writing/S'15 LSTM/methods.tex
Cleanup, citations, etc.

\section{Sentence embedding models for NLI} \label{methods}
\todo{Rewrite in a shorter form, add LSTMs}

@@

>>>>

\section{Sentence embedding models for NLI} \label{methods}

@@

\begin{figure*}[t]
  \centering
\begin{subfigure}[t]{0.29\textwidth}
  \includegraphics[height=1.6in]{fig3.pdf}
  \caption{Training expression size $\le$3.}
  \end{subfigure}~~
\begin{subfigure}[t]{0.29\textwidth}
    \includegraphics[height=1.6in]{fig4.pdf}
  \caption{Training expression size $\le$4.}
  \end{subfigure}~~
\begin{subfigure}[t]{0.4\textwidth}
      \includegraphics[height=1.6in]{fig6.pdf}
  \caption{Training expression size $\le$6.}
\end{subfigure}
  \caption{Results on three experiments with increasingly rich training sets. The horizontal axis on each graph divides the test set data points (expression pairs) into bins by the number of logical operators in the more complex of the two expressions in the pair.}
  \label{prop-results} 
\end{figure*}
